Clouds and Radiation in a mock-Walker Circulation

### 2019-10-31 Silvers_WalkerCell.tex
added reference for Bjerknes 69 and a small amount of text

  \item{Citation of Walker, Bjerness, and Johnson et al. papers to set the stage}

@@

  \cite{Bretherton2005, Muller2012}.
  %Bretherton et al. 2005, Muller and Held, 2012)
  }

>>>>

  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus/congestus, and congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been extensively studies (review paper?).  The circulation first 
  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep convection to the 
  eastern Pacific region which tends to be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  This circulation
   has come to be 
  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations (Walker, Bjerknes), theory (Geisler, 1981), 
  or modeling studies (Bretherton et al., 2006; Wofsy and Kuang, 2012).  The modeling studies have compared theoretical models with cloud
  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker Circulation with 
  simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}

@@

  \cite{Bretherton2005, Muller2012}.}
